Layered Formal Verification of a TCP/IP Stack

### 2021-06-03 SecDev21/paper.tex
removing a todo
fixing the memory leak text

\todo[inline]{KG:pending contributions list and fixing the next paragraph. Will be fixed when the rest of the paper is finalized.}

@@

\todo[inline]{KG: fixed up to here}

@@

Thanks to the pointer ownership policy adopted by SPARK and detailed in
section~\ref{sec:pointers}, we have found that a memory leak can happen when
the connection has been closed and the buffer are cleaning.

\subsubsection{Violation of the TCP protocol}

>>>>

%\todo[inline]{KG:pending contributions list and fixing the next paragraph. Will be fixed when the rest of the paper is finalized.}

@@

@@

The pointer ownership policy of SPARK, detailed in \Cref{sec:pointers}, enabled the detection of a memory leak when a socket closes. This was present due to partially freeing the memory allocated for the buffer that stores the incoming segments. This bug was due to using the wrong library function call to free the memory. SPARK ownership policy detected this because, after the call to this function, the pointer to the buffer was declared not own anymore, but the memory pointed by that pointer was partially deallocated.

\todo[inline]{KG: fixed up to here}
\subsubsection{Violation of the TCP protocol}
